A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-29 manuscript.Rmd
move sentance
preregistrations are not always reproducible

We argue that a preregistration as code (PAC) is an excellent planning tool that offers several benefits over traditional preregistration.
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results before they gather data, were the results are initially based on simulated data.

@@

We discuss PAC as an example of how a robust reproducibility standard has the potential to benefit research projects throughout the whole research process, starting at the beginning, with planning a study.

@@

Why are PAC and reproducibility related?
A reproducible script is supposed to work on the same data at a later point in time.
PAC requires a script to work on different data at a later point in time, a property we call "reusability".
This property is based on reproducibility, but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] so it is build-for-reuse [@al-badareenReusableSoftwareComponents2010].
Reusability promises a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].

>>>>

We argue that a preregistration as code (PAC) is an excellent planning tool that offers several benefits over traditional preregistration.
For a PAC, researchers write a reproducible, dynamically generated manuscript including the sections Introduction, Methods, and Results before they gather data, were the results are initially based on simulated data.
We discuss PAC as an example of how a robust reproducibility standard has the potential to benefit research projects throughout the whole research process, starting at the beginning, with planning a study.

@@

@@

Why are PAC and reproducibility related?
One the one hand, preregistrations are plagued by nonreproducibility like any other research outcome.
@bakkerRecommendationsPreregistrationsInternal2020 found from the 210 preregistrations they investigated 174 (67%) included a formal power analysis but from these only 34 (20%) provided enough information to theoretically reproduce the power analysis.
Even researcher who have gone to great length in submitting a script in their preregistration sometimes inexplicably fail to reproduce their own results.
@steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).

On the other hand have PACs greater requirements for reproducibility than a simple analysis script.
A reproducible script is supposed to work on the same data at a later point in time.
PAC requires a script to work on different data at a later point in time, a property we call "reusability".
This property is based on reproducibility, but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] so it is build-for-reuse [@al-badareenReusableSoftwareComponents2010].
Reusability promises a wide range of applications, among them PAC [possibly submitted as a registered report @nosekRegisteredReports2014; @chambersWhatNextRegistered2019], Direct Replication[@simonsValueDirectReplication2014], fully automated living metanalysis [@elliottLivingSystematicReviews2014], Executable Research Articles [@elifesciencespublicationsELifeLaunchesExecutable2020], and other innovations like the live analysis of born open data [@rouderWhatWhyHow2016; @kekecsRaisingValueResearch2019].
